agdarsec -- Total Parser Combinators

### 2017-10-27 doc/paper/main.tex
[ more ] schainl

\remark{Non-compositionality} The higher-order parser \AF{some}
expects a \emph{fully} defined parser as an argument. This makes
it impossible to use it as one of the building blocks of a larger,
recursive parser. Ideally we would rather have a combinator of
type \mbox{\AF{[} \AF{Parser} \AB{A} \AF{⟶} \AF{Parser} (\AF{List$^+$} \AB{A}) \AF{]}}.
This will be adressed in the next subsection.
\medskip{}

@@

We naturally want to include a safe variant of this combinator in our
library. However this definition relies on the ability to simply use
\textit{return} in case it's not possible to parse an constructor
additional constructor and argument and that is something we simply
don't have access to.

>>>>

\remark{Non-compositionality}\label{parser:some} The higher-order parser \AF{some}
expects a \emph{fully} defined parser as an argument. This makes
it impossible to use it as one of the building blocks of a larger,
recursive parser. Ideally we would rather have a combinator of
type \mbox{\AF{[} \AF{Parser} \AB{A} \AF{⟶} \AF{Parser} (\AF{List$^+$} \AB{A}) \AF{]}}.
This will be adressed in the next subsection.
\medskip{}

@@

We naturally want to include a safe variant of this combinator in our
library. However this definition relies on the ability to simply use
\textit{return} in case it's not possible to parse an additional
constructor and argument and that is something we simply don't have
access to. This forces us to find the essence of \parser{rest}, the
auxiliary definition used in \parser{hchainl}: its first argument is
not just a value, it is a \AR{Success} upon which it builds until it
can't anymore and simply returns.

We define \parser{schainl} as the fixpoint of either \parser{rest}
(whose definition we omit here) or the \AR{Success} that was passed
as an input (the function \AF{\_::$^{r}$} appends a single element
at the end of a list).

\agrab{Text/Parser/Combinators}{schainl}

The type of \AF{rest} may look intimidating but it has this shape because
we build a list of \AR{Success}es at the \emph{same} index as the input
\AR{Success} and \AR{Parser} which will make this combinator compositional
(as opposed to \parser{some} defined in Section~\ref{parser:some}). Ultimately
all of this complexity only shows up in the implementation of our library:
the end user can happily ignore these details.
